\singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants determine interactions with floral visitors

### 2022-06-14 Manuscript/Lanuza_et_al_2021.Rmd
edits

Although the negative correlation between flower number and flower size has received substantial attention [worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a two-trait approach. Here, we provide support to this evidence with a great diversity of phylogenetic lineages (170 families and over 1000 species) and show that other reproductive and plant size and form related traits also covariate along this axis. For example, most species with unisexual flowers (14% of all species) were concentrated in the trait space and were associated with species with woddy life forms (i.e., trees and shrubs) with high flower number. This empirical evidence corroborates the idea that approximately 10% of species have separation of sexes [@barrett2002] and that breeding systems are associated with specific life forms [@petit2006]. The pollinator dependence - floral display axis

>>>>

Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1000 species) within a multitrait context. Although the negative correlation between flower number and flower size has received substantial attention [worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a two-trait approach. We found support to this trait association and show that other reproductive and plant size and form related traits also covariate along this axis. For example, our study complements previous evidence that links breeding systems and life forms [@petit2006; friedman2020] by showing that most species with unisexual flowers were concentrated in the trait space with woody life forms with high flower number. Similarly, the second axis of reproductive trait variation also confirmed the previously described positive association between outcrossing rate and floral display [@goodwillie2010]. Thus, as expected species with higher pollination dependende had greater allocation to flower number or flower size.

Although the negative correlation between flower number and flower size has received substantial attention [worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a two-trait approach. Here, we provide support to this evidence with a great diversity of phylogenetic lineages (170 families and over 1000 species) and show that other reproductive and plant size and form related traits also covariate along this axis. For example, our study complements previous evidence that links breeding systems and life forms [@petit2006; friedman2020] by showing that most species with unisexual flowers were concentrated in the trait space with woody life forms with high flower number. Similarly, the second axis of reproductive trait variation also provided solid evidence for the previously described positive association between outcrossing rate and floral display [@goodwillie2010].

Despite floral rewards not being included in the main analysis because there was insufficient data, we found on an additional exploration that as expected

we found that most species with unisexual flowers (14% of all species) were concentrated in the trait space and were associated with woody life forms with high flower number. These findings are consistent with the idea that approximately 10% of Angiosperms have separation of sexes [@barrett2002] and that breeding systems are associated with specific life forms [@petit2006; friedman2020]. Moreover, our findings of the positive association between pollinator dependence and floral display confirms previous evidence that shows across 154 flowering plants that species with higher outcrossing rates allocate more resources to attraction [@goodwillie2010].

greater allocation of resources to attraction for species with higher outcrossing rates [@goodwillie2010].

14% of plant species in our dataset had unisexual flowers

14% of plant species in our dataset had unisexual flowers and they were concentrated in the trait space and associated with woody life forms with high flower number. Our findings of the positive association between pollinator dependence and floral display confirms previous evidence that shows greater allocation of resources for species with higher outcrossing rates [@goodwillie2010].

provide additional support to the positive correlation between pollinator dependence and floral display [@]

For example, most species with unisexual flowers (14% of species of our dataset) were concentrated in the trait space and were associated with woody life forms and high flower number. These findings support the idea that approximately 10% of Angiosperms have separation of sexes [@barrett2002] and that breeding systems are associated with specific life forms [@petit2006]. Our results also highlight the existence of a reproductive axis where floral display and pollinator dependence are positively correlated

with species with woddy life forms (i.e., trees and shrubs) with high flower number. This empirical evidence corroborates the idea that approximately 10% of species have separation of sexes [@barrett2002] and that breeding systems are associated with specific life forms [@petit2006]. The pollinator dependence - floral display axis
